%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Employment}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
\cventry
    {Co-Technical Director} % Job title
    {Electronic Field Notebooks PTY LTD} % Organization
    {2020 -- Present} % Date(s)
    {Sydney, Australia} % Location
    {\begin{cvitems}%
    \item {Product Owner for Fieldmark}
    \item {Technical lead and DevOps lead for Fieldmark.}
    \item {Founder, Electronic Field Notebooks.}
    \end{cvitems}%
    }

\cventry
    {Solutions Architect (Digital Humanities) -- Professional} % Job title
    {Macquarie University} % Organization
    {2018 -- Present} % Date(s)
    {Sydney, Australia} % Location
    {\begin{cvitems}%
    \item {Collected and analysed hundreds of thousands of social media posts using Natural Language Processing from right wing extremist accounts in New South Wales and provide policy suggestions for senior civil servants in NSW.}
    \item {Worked with colleagues to design, develop, and deploy data pipelines and outputs for their research. \href{https://onwork.edu.au}{Onwork.edu.au}, ARC funded, twice featured in The Australian, is an ongoing collaboration with Prof JP Deranty, transforming a 1000+ citation database into a website.}
    \item {Developed Data Management standards and online courseware in compliance with the new NHMRC rules with the Macquarie University Research Integrity Secretariat.}
    % \item {Worked with Prof Sean Brawley as the Data Architect and Senior Developer for his Course Health Check dashboard. }
    \item {Organised and was a lead instructor for 10+ Software Carpentry and Carpentries Instructor Training workshops.}
    \item {Won a U.S. Challenge.gov Prize for designing a innovative offline-capable field data collection framework with A/Prof Shawn Ross.}
    \item {Brought Macquarie University on as a partner on Google Arts and Culture.}
    \item {Collaborated with Ubisoft and Google on the Hieroglyphics Initiative/Fabricius.}
    \item {Supported academics and students across the faculty to design, deliver, and deploy technical solutions to academic research problems.}
    \end{cvitems}%
    }
    \cventry
    {Technical Director, Field Acquired Information Management Systems (FAIMS) Project -- Professional} % Job title
    {Macquarie University} % Organization
    {2015 -- 2018} % Date(s)
    {Sydney, Australia} % Location
    {\begin{cvitems}%
    \item {Supported a major code update and capability extension for FAIMS 2.}
    \item {Designed, edited, and typeset a grant-funded ``User to Developer Guide``.}
    \item {Provided emergency remote support for teams using FAIMS in the field worldwide.}
    \item {Deployed 47 field-ready modules with custom data export capabilities into CSVs, shapefiles, JSON, Con\TeX{}t, and KML.}
    \item {Maintained and supported virtual machines for all FAIMS infrastructure.}
\end{cvitems}}
 
\cventry
    {Data Architect, Federated Archaeological Information Management Systems (FAIMS) Project -- Academic/Professional} % Job title
    {UNSW Australia} % Organization
    {2012 -- 2015} % Date(s)
    {Sydney, Australia} % Location
    {\begin{cvitems}%
    \item {Directed FAIMS development goals for a successful mobile app launch.}
    \item {Deployed seven field modules and exporters to convert data into CSVs and shapefiles.}
    \item {Developed a domain-key normal form data structure, XML and XSLT transforms for data specification, and appropriate database queries to convert XML into a spatially enabled SQLite database.}
    \item {Administered all FAIMS infrastructure, designing and managing project virtual machines and management infrastructure.}
    \end{cvitems}}   

% \cventry
%     {Adjunct Professor, Department of Information Technology} % Job title
%     {Rochester Institute of Technology} % Organization
%     {2012 -- 2012} % Date(s)
%     {Rochester, New York, United States} % Location
%     {\begin{cvitems}%
%     \item {Instructor for undergraduate units.}
%     \end{cvitems}}   

% \cventry
%     {Tutor, School of Information Systems \& Technology Management} % Job title
%     {UNSW Australia} % Organization
%     {2008 -- 2009} % Date(s)
%     {Sydney, Australia} % Location
%     {\begin{cvitems}%
%     \item {Tutor and unit designer.}
%     \end{cvitems}}      

% \cventry
%     {Adjunct Professor, Department of Information Technology} % Job title
%     {Rochester Institute of Technology} % Organization
%     {2007 -- 2008} % Date(s)
%     {Rochester, New York, United States} % Location
%     {\begin{cvitems}%
%     \item {Significant experience teaching in hearing and hard of hearing combined units. All units taught had live American Sign Language interpreter support.}
%     \item {Taught and convened undergraduate and graduate level Information Technology units in databases and requirements assessment.} 
%     \item {Helped to develop the Data Warehousing graduate unit.}
%     \end{cvitems}}
    
% \cventry
%     {Graduate Assistanceship in Databases} % Job title
%     {Rochester Institute of Technology} % Organization
%     {2006 -- 2007} % Date(s)
%     {Rochester, New York, United States} % Location
%     {\begin{cvitems}%
%     \item {Designed laboratory work and virtualisation strategies for the Data Warehousing unit.}
%     \end{cvitems}}     
%---------------------------------------------------------
%   \cventry
%     {} 
%     
%     
%     
%     {
%       
%     }

\end{cventries}
